Blocking-resistant communication\\through domain fronting

### 2014-07-17 docs/meek.tex
Include fronting figure.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{fronting}
\caption{
Domain fronting uses different domain names at different layers of communication.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor but meaningful to the CDN or web service,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}
